Everthing you wanted to know about PanDA but were truly truly afraid to ask

### 2016-09-19 paper.tex
Changed the path of the figures
First draft workflow/workload and related definitions. Ongoing.

\begin{itemize}
  \item Problem that has been solved: executing many applications on heterogeneous distributed resources.
  \item Why are WMS needed?
  \item Increasing importance of WMS w.r.t complex and scalable applications on heterogeneous distributed resources.
  \item \ldots
  \item Overview/Summary of paper.
\end{itemize}

@@

\begin{itemize}
  \item Brief overview of distributed CI.
  \item Workload vs Workflow
  \item Distinguish between WFMS and WLMS!!!!
  \begin{itemize}
    \item Role of Workload MS: help “hide” and federate heterogeneous resources.
  \end{itemize}
\end{itemize}

@@

\begin{itemize}
  \item Other workload management systems (WMS) (not exclusive)
  \begin{itemize}
    \item glidein-WMS
    \item Dirac
    \item ALICE-AlieN
  \end{itemize}
  \item Comparison and contrast
  \item Core features of a general WMS, i.e., minimal complete model of a WMS.
\end{itemize}

@@

\begin{itemize}
  \item PanDA WMS
  \begin{itemize}
    \item State Diagrams
    \item Control Flow Diagrams
    \item Software Module and Architecture diagrams.
  \end{itemize}
  \item PANDA Pilot
\end{itemize}

>>>>

\begin{enumerate}
  \item Problem that has been solved: executing many applications on heterogeneous distributed resources.
  \item Why are WMS needed?
  \item Increasing importance of WMS w.r.t complex and scalable applications on heterogeneous distributed resources.
  \item \ldots
  \item Overview/Summary of paper.
\end{enumerate}

@@

\begin{enumerate}
  \item Brief overview of distributed CI.
  \item Workload vs Workflow. (DONE)
  \item Distinguish between WFMS and WLMS.
  \begin{enumerate}
    \item Role of Workload MS: help ``hide'' and federate heterogeneous resources.
  \end{enumerate}
\end{enumerate}

\paragraph*{Workload Vs Workflow} The term ``workflow'' is used in many
disciplines with different meaning. In the field of scientific computing,
``workflow'' assumes different meanings depending on the characteristics of
the computation, of the software tools used to support this computation, and
of the resources on which it is performed. Further, a workflow may indicate a
whole application, a description of the computational process of that
application or, more commonly, a series of tasks related by data
dependences.

The lack of a consistent and shared definition of ``workflow'' hinders the
understanding of its properties and its relations with related concepts. For
example, we need to clarify the difference between ``workflow'', ``workload'',
``task'', or ``job'' but also between workflow template and instance, or
data-flow and control-flow. This clarification is precondition to specify
properly the design of software systems that support the execution of
scientific applications.

In this paper, a workflow is a set of tasks alongside a description of their
properties and relations. Each task may have an arbitrary number of properties
like number of cores, executables, or input/output files. Tasks may have
precedence relations depending on their data dependences or any other type of
dependency mandated by the application algorithms. Tasks with precedence
relations have to be executed serially, otherwise tasks can be executed
concurrently. A workload is defined as a set of tasks that can be executed
concurrently. As such, a workflow can be composed by a set of workloads.

The terms ``task'' and ``job'' are also used inconsistently across communities
that perform scientific computing. In this paper, a task is a \ldots
\mtnote{Are we going to use task and job as defined in Jedi and Panda Server?}

Usually, workflows are represented as graphs where tasks are vertices and
their relations edges~\cite{}. Often, graphs are supposed to be acyclic but
graphs with cycles have been used to represent workflows of workflows. In this
paper, a workflow template is a type of graph while a workflow instance is a
type of graph with a specific set of vertices and edges. Further, a graph is
``abstract'' when no resource properties are available for all vertices,
``concrete'' otherwise~\cite{}.

The distinction between an abstract and concrete graph highlights an important
element of the execution process of a workflow. Workflows can be specified
without indicating on what resources they should be executed. Accordingly, an
abstract workflow can be interpreted as a formal description of the
requirements for the workflow execution. Once these requirements are matched
by a set of resource capabilities, an abstract workflow becomes a concrete
workflow, i.e. a formal description of the workflow execution process and its
execution environment.

@@

\begin{enumerate}
  \item Other workload management systems (WMS) (not exclusive)
  \begin{enumerate}
    \item glidein-WMS
    \item Dirac
    \item ALICE-AlieN
  \end{enumerate}
  \item Comparison and contrast
  \item Core features of a general WMS, i.e., minimal complete model of a WMS.
\end{enumerate}

@@

\begin{enumerate}
  \item PanDA WMS
  \begin{enumerate}
    \item State Diagrams
    \item Control Flow Diagrams
    \item Software Module and Architecture diagrams.
  \end{enumerate}
  \item PANDA Pilot
\end{enumerate}
